Weighted Model Counting Without Parameter Variables

### 2021-05-08 doc/paper3/box.tex
Writing about experiments
Preparing the camera-ready version

% Created by tikzDevice version 0.12.3.1 on 2021-02-28 16:52:48
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (173.45,144.54);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 46.48, 65.20) -- ( 54.75, 65.20);

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 70.99, 66.74) -- ( 79.26, 66.74);

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 95.50, 66.74) -- (103.77, 66.74);

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] (120.01, 57.40) -- (128.28, 57.40);

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] (144.97, 53.85) -- (161.51, 53.85);
\definecolor{drawColor}{gray}{0.70}

@@

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-05-08 15:35:22
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (173.45,144.54);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (173.45,144.54);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 46.48, 65.31) -- ( 54.75, 65.31);

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 70.99, 66.85) -- ( 79.26, 66.85);

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 95.50, 66.85) -- (103.77, 66.85);

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] (120.01, 57.43) -- (128.28, 57.43);

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] (144.97, 53.86) -- (161.51, 53.86);
\definecolor{drawColor}{gray}{0.70}

@@

\end{document}
